Replicator-mutator and noise-perturbed replicator dynamics

### 2014-09-29 snippets/data_exploration/data_exploration_tmp.Rmd
results section sec com

pairs(~ Number.of.states + Impairment + Tolerance + Speaker.entropy + Hearer.entropy + 
        Speaker.Voronoiness + Hearer.Voronoiness +
        Speaker.informativity + Hearer.informativity + Expected.utility + Iterations +
        Speaker.Convex.Cat, data=ds)
```

@@

@@

sp + facet_grid(variable ~ Tolerance, scales="free")

@@

@@

>>>>

pairs(~ Speaker.entropy + Hearer.entropy + Speaker.Voronoiness + Hearer.Voronoiness +
        Speaker.informativity + Hearer.informativity + Expected.utility +
        Speaker.Convex.Cat, data=ds)
```

@@

ds = data[,c("Number.of.states", "Impairment", "Tolerance", 
             "Speaker.entropy", "Hearer.entropy",
             "Speaker.informativity",
             "Speaker.Voronoiness", "Hearer.Voronoiness",
             "Expected.utility")]

dm = melt(ds, id.vars = c("Number.of.states", "Impairment", "Tolerance"))

@@

sp = sp + facet_grid(variable ~ Tolerance, scales="free")

show(sp)

pdf("~/Desktop/data/svn/vagueness-games/paper/plots/MeanMetrics.pdf", width=8, height = 8)
show(sp)
dev.off()

@@

Entropy
-------

```{r fig.width=5, fig.height=5}
cor.test(data$Speaker.entropy, data$Hearer.entropy)
qplot(data$Speaker.entropy, data$Hearer.entropy) + geom_smooth(method=lm)
```

@@

Voronoiness
-------

```{r fig.width=5, fig.height=5}
cor.test(data$Speaker.Voronoiness, data$Hearer.Voronoiness)
qplot(data$Speaker.Voronoiness, data$Hearer.Voronoiness) + geom_smooth(method=lm)
```

Percentage of Converged and Convex strategies
---------------------------------------------

data$Converged = data$Iterations < 201
data$Convex = data$Speaker.Convex.Cat

ds = data[,c("Number.of.states", "Impairment", "Tolerance", 
             "Converged", "Convex")]

dm = melt(ds, id.vars = c("Number.of.states", "Impairment", "Tolerance"))

sp = ggplot(dms, aes(x=factor(Impairment), y = value)) 
sp = sp + geom_bar(aes(fill = variable), color = "black", stat="identity", position= position_dodge(0.4), width = 0.3)
sp = sp + facet_grid(Number.of.states ~ Tolerance, scales="free")

show(sp)

pdf("~/Desktop/data/svn/vagueness-games/paper/plots/CategoricalMeasures.pdf", width=8, height = 6)
show(sp)
dev.off()

### 2014-09-29 snippets/exploring_uniformity_from_impairment/uniformity.Rmd
results section sec com

```{r echo = FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=7}
  show(sPlot)
```

>>>>

```{r echo = FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=7}
  show(sPlot)

pdf("~/Desktop/data/svn/vagueness-games/paper/plots/AverageEUinGroups.pdf", height = 6, width = 8)
show(sPlot)
dev.off()
